---
title: "Portfolio 10 -- Recreating a Bar Plot"
author: "Ryan Wheat"
date: "05/05/2023"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, include = FALSE}
library(tidyr)
library(tidyverse)
library(dplyr)
library(haven)
library(gt)
```


```{r get-data, include = FALSE}

Item_Ratings <- read_sav("//10.4.6.5/psychology/labs/honestyproject/Empirical Activities/Item-ratings/Data/Item Ratings.sav")

```

##Background

I've done some relatively lengthy portfolios recently, so today, I'm going to take it down a notch: I'm going to try to make some visuals using ggplot.

First, I'm going to utilize data from my first year project for this purpose. In this study, we examined the content validity of a new honesty scale -- the Truthful Communication Scale (TCS) -- by comparing the face validity of its items against those of another "honesty" scale, Honesty-Humility (HH). 

Participants were asked to rate the extent to which each item from both scales reflected (1) truthfulness, (2) manipulativeness, (3) law-breaking, (4) greed, (5) modesty. Lets plot those results.

```{r overall-truthfulness}

#create long dataset to compare truthfulness ratings

Item_Ratings_Long1 <- Item_Ratings %>%
  mutate(Participant = c(1:152)) %>%
  select(206, 200:205) %>%
  pivot_longer(!Participant, names_to = "Scale", values_to = "Avg_Tru_Rating")

#make new variable with better label for plotting

Item_Ratings_Long1 <- Item_Ratings_Long1 %>%
  mutate(ggplot_name = case_when(Scale == "Sin_Tru" ~ "HH Sincerity",
                                 Scale == "Fair_Tru" ~ "HH Fairness",
                                 Scale == "Greed_Tru" ~ "HH Greed-Avoidance",
                                 Scale == "Mod_Tru" ~ "HH Modesty",
                                 Scale == "TCS_Tru" ~ "TCS",
                                 Scale == "HH_Tru" ~ "HH Overall"))

Item_Ratings_Long1$ggplot_name <- factor(Item_Ratings_Long1$ggplot_name, levels = c("TCS", "HH Sincerity", "HH Fairness", "HH Greed-Avoidance", "HH Modesty", "HH Overall"))

#make plot

ggplot(Item_Ratings_Long1, aes(x = ggplot_name, y = (Avg_Tru_Rating / 152), fill = ggplot_name)) +
  geom_col() +
  theme_bw() +
  coord_cartesian(ylim = c(0, 3)) +
  scale_fill_manual(label = NULL, values = c("black", "gray80", "gray56", "gray63", "gray50", "gray75")) +
  labs(title = "Truthfulness Item Ratings",
       x = "Scale",
       y = "Mean Informativeness About Truthfulness",
       fill = NULL)
```

This plot shows that TCS items are more face-valid for truthfulness than HH items are. But what about comparing the difference between the validity of items on truthfulness vs. other relevant constructs?

I created a variable to reflect such a difference called "Pure Truthfulness." This is a difference score, such that ratings above zero on this variable indicate that an item reflects truthfulness MORE THAN some other construct (e.g., manipulativeness, law-breaking, greed, modesty) that may ostensibly be related to these items.

```{r pure-truthfulness}

#create long dataset to compare pure truthfulness ratings

Item_Ratings_Long2 <- Item_Ratings %>%
  mutate(Participant = c(1:152)) %>%
  select(206, 194:199) %>%
  pivot_longer(!Participant, names_to = "Scale", values_to = "Avg_Pure_Rating")

#make new variable with better label for plotting

Item_Ratings_Long2 <- Item_Ratings_Long2 %>%
  mutate(ggplot_name = case_when(Scale == "Sinpure" ~ "HH Sincerity",
                                 Scale == "Fairpure" ~ "HH Fairness",
                                 Scale == "Greedpure" ~ "HH Greed-Avoidance",
                                 Scale == "Modpure" ~ "HH Modesty",
                                 Scale == "TCpure" ~ "TCS",
                                 Scale == "HHpure" ~ "HH Overall"))

Item_Ratings_Long2$ggplot_name <- factor(Item_Ratings_Long2$ggplot_name, levels = c("TCS", "HH Sincerity", "HH Fairness", "HH Greed-Avoidance", "HH Modesty", "HH Overall"))

#make plot

ggplot(Item_Ratings_Long2, aes(x = ggplot_name, y = (Avg_Pure_Rating / 152), fill = ggplot_name)) +
  geom_col() +
  theme_bw() +
  coord_cartesian(ylim = c(-3, 3)) +
  scale_fill_manual(label = NULL, values = c("black", "gray80", "gray56", "gray63", "gray50", "gray75")) +
  labs(title = "Truthfulness Item Ratings",
       x = "Scale",
       y = "Mean Informativeness About Truthfulness",
       fill = NULL)
```

